\papertitle

### 2012-10-13 manuscript.tex
Drafted cooperative visual servoing description section.

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Eq.~\ref{eq:emission_model}) effectively performs \naive

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}

>>>>

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Eq.~\ref{eq:emission_model}) effectively performs.

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
Remote guidance of the H$^2$Bird is performed by commanding relative changes in the
reference orientation. With estimates of the vehicle pose, we calculate an altitude
error and horizontal error. Incremental changes to the H$^2$Bird pitch and yaw are
then commanded according to a PID control law, with positive altitude error
corresponding to negative incremental pitches and positive horizontal error
corresponding to negative incremental yaw. The controller integrator term is windowed
to prevent windup when the bird is being launched, and the derivative term was tuned
by hand to dampen oscillations associated with the system latency [?].
